CG Methylation RPKM 1->4
========================================================

```{r fig.width=7, fig.height=5}
library(ggplot2)
library(grid)

file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CG_all_1.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, 
       aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% Methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(14,84)
```


Are these changes significant

```{r}
library(PMCMR)
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CG_all_2.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% Methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(14,84)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CG_all_3.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% Methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(14,84)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CG_all_4.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% Methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(14,84)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

CHG Methylation RPKM 1->4
========================================================

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHG_all_1.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,35)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHG_all_2.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,35)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHG_all_3.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,35)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHG_all_4.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,35)
```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHH_all_1.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, 
       aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,21)

```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```
CHH Methylation RPKM 1->4
========================================================
```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHH_all_2.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,21)

```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHH_all_3.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,21)

```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```

```{r fig.width=7, fig.height=5}
file_name = "/Users/gturco/Documents/Data/Sorg/TSS/rpkm_new/tissue/Tissue/CHH_all_4.txt"
x = read.table(file_name, col.names=c("pos","freq","mtype"))
x$mtype <- factor(x$mtype, levels = c("root","shoot","vascular","nonvascular"))
ggplot(data=x, aes(x = pos, y = freq * 100 ,group=mtype, color = mtype)) +  geom_line(size = .3) +
  theme_classic() + theme(text=element_text(size=20))    +  theme(legend.position ="none", text=element_text(size=7), panel.margin = unit(0, "cm"), plot.margin = unit(c(0, 0, 0.01, -0.1), "cm"),axis.ticks = element_line(size = 0.1), axis.line = element_line(size = 0.1), axis.ticks.length = unit(0.05, "cm"), axis.ticks.margin =unit(0, "cm")) + xlab(NULL) + ylab("% methylation") + scale_colour_manual(values=c("#c6141c","#fccb0c","#009987","#3261a8")) + ylim(5,21)

```


Are these changes significant

```{r}
kruskal.test(freq ~ mtype, data = x) 
posthoc.kruskal.nemenyi.test(freq ~ mtype, data=x, dist="Tukey")

```